Optimal management of a stochastically varying population when policy adjustment is costly

### 2015-01-23 manuscripts/manuscript.Rmd
need to debug figure4 data.frame

```{r Figure_4, fig.cap="Variance and autocorrelation of harvest dynamics, as a function of the penalty coefficient.  Adjustment penalty is calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs.", fig.height=4, fig.width=8, cache=fig.cache, dev=c("pdf", "svg", "png")}

>>>>

```{r Figure_4, fig.cap="Variance and autocorrelation of harvest dynamics, as a function of the penalty coefficient.  Adjustment penalty is calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs.", fig.height=6, fig.width=4, cache=fig.cache, dev=c("pdf", "svg", "png")}
